---
title: "Merging clean datasets"
author: Pau Grau
date: 23 de desembre de 2019
output: html_document

---

#Load packages
```{r}
if (!require(repmis)) { install.packages(repmis); library(repmis) } 
if (!require(httr)) { install.packages(httr); library(httr) } 
if (!require(readr)) { install.packages(readr); library(readr) } 
if (!require(dplyr)) { install.packages(dplyr); library(dplyr) } 
if (!require(tidyverse)) { install.packages(tidyverse); library(tidyverse) } 
if (!require(countrycode)) { install.packages(countrycode); library(countrycode) } 
if (!require(haven)) { install.packages(haven); library(haven) } 



```
# Clean CLEA
Keep only district information (not party). Remove cases older than 1945. Build variance (varmag), SD(sdmag) and mean(memag) magnitude.
```{r}
load("C:/Users/Pau Grau/Desktop/clea_lc_20190617.rdata")
clea <- select(clea_lc_20190617, 1:11)
head(clea)
clea<-clea %>% distinct() 
head(clea)

clea <- subset(clea, clea$yr>1945)
clea$mag[clea$mag<0] <- "."

clea <- select(clea, -1:-2)
head(clea)

clea$mag <- as.numeric(as.character(clea$mag))

var <- aggregate(clea$mag,by=data.frame(clea$ctr,clea$ctr_n, clea$yr, clea$mn), var, na.rm=TRUE)

mean <- aggregate(clea$mag,by=data.frame(clea$ctr,clea$ctr_n, clea$yr, clea$mn), mean, na.rm=TRUE)

clea1 <- merge(mean,var, by=c("clea.yr", "clea.ctr", "clea.mn"))

clea1 <- select(clea1, -6)
clea1$varmag <- as.numeric(as.character(clea1$x.y))
clea1$sdmag <- sqrt(clea1$varmag)
clea1$memag <- as.numeric(as.character(clea1$x.x))

clea1 <- select(clea1, -5:-6)
clea1$UN <- clea1$clea.ctr
clea1$country <- clea1$clea.ctr_n.x
clea1$year <- clea1$clea.yr
clea1$month <- clea1$clea.mn
clea1<- clea1[,-1:-4]

write.csv2(clea1, file="clea1.csv")
```
# Import data and export them as csv in a unified format

```{r}
library(haven)
AlesinaCOW <- read_dta("C:/Users/Pau Grau/Downloads/Alesina+COW (2).dta")
AlesinaCOW <- AlesinaCOW[-c(216:1085), ]
AlesinaCOW$UN <- countrycode::countrycode(AlesinaCOW$country, "country.name", "un")
AlesinaCOW$cow <- countrycode::countrycode(AlesinaCOW$country, "country.name", "cown")

write.csv2(AlesinaCOW, file="AlesinaCowUN.csv")
```

# Download data from github
MANUALLY UPLOADED TO GITHUB."https://github.com/pgrau7/ES-0/blob/master"
```{r}
alesina <- readr::read_csv2(url("https://raw.githubusercontent.com/pgrau7/ES-0/master/Merging datasets/AlesinaCowUN.csv"))

golder <- read.csv(url("https://raw.githubusercontent.com/pgrau7/ES-0/master/Merging datasets/es_data-v3.csv"))

clea <- readr::read_csv2(url("https://raw.githubusercontent.com/pgrau7/ES-0/master/Merging datasets/clea1.csv"))
```
UPLOAD COW TO UN, which has more codes.
```{r}
alesina$UN <- countrycode::countrycode(alesina$country, "country.name", "un")
golder$country <- as.character(golder$country)
golder$UN <- countrycode::countrycode(golder$country, "country.name", "un")
clea$country <- as.character(clea$country)
clea$UN <- countrycode::countrycode(clea$country, "country.name", "un")
```

Golder is Base. I should delete presidential elections (as it might be problematic when merging, for having two elections in the same year/country).
```{r}
golder <- subset(golder, !(presidential == "1"))
```

- Add CLEA
```{r}
golder$country <- as.character(golder$country)
clea$country <- as.character(clea$country)

golderclea1 <- merge(golder,clea,by=c("UN", "year", "month"))
```
- Add Alesina
```{r}
goldercleaalesina <- merge(golderclea1, alesina, by=c("UN"))
```
EXPORT (and upload manually)
```{r}
write.csv2(goldercleaalesina, file="FINAL_DATA.csv")
```

# Create the clean dataset
Import dataset from https://raw.githubusercontent.com/pgrau7/ES-0/master/FINAL_DATA.csv.
```{r, echo=FALSE, message=FALSE, warning=FALSE}
mydata <- read_csv2(url("https://raw.githubusercontent.com/pgrau7/ES-0/master/Merging datasets/FINAL_DATA.csv"))
mydata$EthAl <- as.numeric(mydata$EthAl)
```
Select our variables and build a reduced dataset.
```{r, echo=FALSE, message=FALSE, warning=FALSE}
myvars <- c("country.x","year", "month","elec_id", "enep", "seats", "memag", "varmag", "EthAl", "uppertier", "upperseats")
myvars1 <- c("enep", "seats", "memag", "varmag", "EthAl", "uppertier", "upperseats")
newdata <- mydata[myvars]
```

###Preliminar Formatting
```{r, echo=FALSE, message=FALSE, warning=FALSE}
newdata$enep[mydata$enep==-99] <- NA
newdata$uppertier[mydata$uppertier==-99] <- NA
newdata$upperseats <- as.numeric(newdata$upperseats)
newdata$upperseats[mydata$upperseats==-99] <- NA
```

###Bivariant statistics
To do it, I'll use GGplot2 and GGally^[John W Emerson, Walton A Green, Barret Schloerke, Jason Crowley, Dianne Cook, Heike Hofmann, Hadley Wickham. The Generalized Pairs Plot. Journal of Computational and Graphical Statistics, vol. 22, no. 1, pp. 79-91, 2012.]. This plot allows us to see that memag, marmag and uppertier are highly skewed to the left. 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
GGally::ggpairs(newdata[,-1:-4], title="Bivariant descriptive statistics")
```
In order to meet the normality assumption needed in regressions, we will log1p-transform these variables. As we have many zeros, we will make the logarithm of x+1.
```{r, echo=FALSE, message=FALSE, warning=FALSE}
attach(newdata)
newdata$logenep <- log1p(enep)
newdata$logseats <- log1p(seats)
newdata$logmemag <- log1p(memag)
newdata$logvarmag <- log1p(varmag)
newdata$logethal <- log1p(EthAl)
newdata$loguppertier <- log1p(uppertier)
newdata$logupperseats <- log1p(upperseats)

GGally::ggpairs(newdata[,-1:-11], title="Bivariant descriptive statistics with loglog1p-transformed data")
```


```{r}
write.csv2(newdata, file="FINAL_DATA1.csv")
```

